Manuscript

### 2018-11-07 manuscript.Rmd

@@

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
  if(nrow(use_data_gdsc_summ) <= 1) {
    gdsc_ttest_res <-  NA
    ticker <- t                                                                                                                                                                                                                icker + 1
    }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
  }

>>>>

```{r}
g2p_druggenelin_p_tally <- g2p %>% group_by(Drug_Gene, group_general_lineage_name) %>% tally()
```

@@

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_summ <- use_data_gdsc %>% count(InG2P)
  if(nrow(use_data_gdsc_summ) <= 1) {
    gdsc_ttest_res <-  NA
    ticker <- ticker + 1
    }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn < 2) { gdsc_ttest_res <-  NA }
  else if(use_data_gdsc_summ[use_data_gdsc_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_lin_p_ttest <- t.test(use_data_gdsc$p ~ use_data_gdsc$InG2P)
    gdsc_ttest_res <- paste0("t = ", round(gdsc_lin_p_ttest$statistic, 3), ", df = ", round(gdsc_lin_p_ttest$parameter, 3), ", p = ", round(gdsc_lin_p_ttest$p.value, 3))
  }
